`r params$set_title`

### 2017-11-27 lib/report.Rmd
progress

> read_chunk('report.R')
```
# https://stackoverflow.com/questions/14796501/is-it-possible-to-call-external-r-script-from-r-markdown-rmd-in-rstudio
# https://stackoverflow.com/questions/23597140/how-to-find-the-percentage-of-nas-in-a-data-frame-using-apply

> ```{r part1}
> annotate with ## @knitr part1 in script
> x %>% summarize_all(funs(sum(is.na(.)) / length(.)))
> ```

>>>>

read_chunk('report.R')
```

```{r part1}
```

```{r part2}
```
